Incentivizing Exploration with Unbiased History

### 2018-10-25 2level.tex
stuff

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};
\end{tikzpicture}

@@

% \begin{itemize}
  \paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
  \OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.} 
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By \Cref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
To facilitate our reasoning, let us imagine there is a tape of length
$T$ for each arm $a$, with each cell containing an independent draw of
the realized reward from the distribution Ber$(\mu_a)$. Then for each
arm $a$ and any $N\in [T]$, we can think of the sequence of the first
$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
reward tape. Define $W^{a,t}_2$ to be the event that the empirical
mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
to be the intersection of these events (i.e.
$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
  confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

>>>>

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};

  \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs of \ALGG in parallel};
\end{tikzpicture}

@@

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.} 
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution Ber$(\mu_a)$. Then for each arm $a$ and any
$N\in [T]$, we can think of the sequence of the first $N$ realized
rewards of $a$ coming from the prefix of $N$ cells in its reward
tape. Define $W^{a,t}_2$ to be the event that the empirical mean of
the first $t$ \swedit{realized rewards in the tape} of arm $a$ is at
most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be
the intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).
By Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

### 2018-10-25 3level.tex
stuff

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
\swcomment{reusable?}
For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]

>>>>

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound,\swcomment{a bit confused about what $t_1$ and $t_2$ mean?}
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]
